Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/methodology.tex
Some editing of methodology

\section{Methodology}
To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market at the time of this study. At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \cite{6_fitbit_2014, 7_time_2014}, the Pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}, and Google Glass \cite{11_wikipedia_2015, 12_turi_2014}. We used these wearable devices, along with other comparable wearable devices on the market, as inspiration for the survey questions.

Our survey contained two main sections.
In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
This was intended to elicit their perception of the severity and impact of the risk.
In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
Our survey design is based on two prior perception studies, as we describe next.
%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.

\subsection{Motivation}
\subsubsection{Smartphone Risk Scenarios}
Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risk scenarios. Participants were asked how upset they would be if a certain action had occurred without permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.

\subsubsection{Technology Risk Perception}
Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}. In their study, participants were asked to separately rate the risks and benefits for those technologies. They were told to think about all people affected by the technology, and to think about long-term vs. short-term risks and benefits. Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 comprehension questions
\item 6 questions about wearable computing scenarios 
\item 2 questions about smartphone scenarios 
\item 2 risk/benefit questions 
\item 15 demographic questions \\[-.8cm]
\end{itemize}

@@

\subsubsection{Wearables Scenarios}
We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}). Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}. Our questions were of the format:

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.47\textwidth]{images/prompt.pdf}
	\caption{An example of a wearable scenario question participants saw while taking the survey.}
	\label{fig:prompt}
\end{figure}

@@

The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared. There were a total of 288 questions in this set, from which we randomly 6 questions for each participant.

>>>>

\section{Methodology}
To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market at the time of this study. At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \cite{6_fitbit_2014, 7_time_2014}, the Pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}, and Google Glass \cite{11_wikipedia_2015, 12_turi_2014}. We used these wearable devices, along with other comparable wearable devices on the market, as inspiration to develop a list of security and privacy risks that users might be concerned about.

We then designed a survey to gauge how severe our participants consider these risks to be.
Our survey contained two main sections.
In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
This was intended to elicit their perception of the severity and impact of the risk.
The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices.
In the other section, we asked participants to compare the risks and benefits of wearable technologies to those of better-understood technologies, following the same methodology from Fischhoff {\it et al.}'s seminal study in risk perception~\cite{Fischhoff}.
%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.

\subsection{Motivation}
\subsubsection{Smartphone Risk Scenarios}
Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risk scenarios. Participants were asked how upset they would be if a certain action occurred without their permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
Our methodology closely follows that study, but with scenarios chosen to shed light on the security and privacy risks of wearable devices.

\subsubsection{Technology Risk Perception}
Fischhoff \etal performed a seminal study of the perceived risks of 30 widely used technologies~\cite{Fischhoff}. In their study, participants were asked to separately rate the risks and benefits for these technologies. They were told to think about all people affected by the technology, and to think about long-term vs. short-term risks and benefits. Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
We apply their methodology to evaluate the perceived risks and benefits of several technologies related to wearable computing.
%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 reading comprehension questions
\item 6 questions about wearable computing scenarios 
\item 2 questions about smartphone scenarios 
\item 2 Fischhoff-style risk/benefit questions 
\item 15 demographic questions \\[-.8cm]
\end{itemize}

@@

\subsubsection{Wearable Scenarios}
We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first (see Figure \ref{fig:prompt}). Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), following Felt \etal\cite{Felt}. Questions were of the form:

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{images/prompt.pdf}
	\caption{An example of a wearable scenario question participants saw while taking the survey.}
	\label{fig:prompt}
\end{figure}

@@

The purpose of these questions was to determine how upset participants would be when data is inappropriately shared, and to understand how their reaction depends upon the type and recipient of the data that is shared.
There were a total of 288 questions in this set, from which we randomly selected 6 questions for each participant.
